High-level cognition during story listening is reflected in high-order dynamic correlations in neural activity patterns

### 2021-05-31 paper/main.tex
updates to supp and main text

\newcommand{\kernelshape}{S1}
\newcommand{\kernelwidth}{S2}
\newcommand{\intact}{S3}
\newcommand{\para}{S4}
\newcommand{\word}{S5}
\newcommand{\rest}{S6}
\newcommand{\pca}{S7}

@@

Overall, we found that we could reliably recover both first-order and
second-order correlations from the synthetic data
(Fig.~\ref{fig:higher_order_sims}).  When the correlations were stable
for longer intervals, or changed gradually (constant, ramping, and
event datasets), recovery performance was relatively high, and we were
better able to recover dynamic first-order correlations than
second-order correlations.  We expected that this would happen, given
that errors in our estimation procedure at lower orders necessarily
propagate to higher orders (since lower-order correlations are used to
estimate higher-order correlations).  Interestingly, we also found
that when the correlations were particularly \textit{un}stable (random
datasets), we better recovered second-order correlations.

>>>>

\newcommand{\kernelshape}{S1}
\newcommand{\kernelwidth}{S2}
\newcommand{\time}{S3}
\newcommand{\features}{S4}
\newcommand{\intact}{S5}
\newcommand{\para}{S6}
\newcommand{\word}{S7}
\newcommand{\rest}{S8}
\newcommand{\pca}{S9}

@@

Overall, we found that we could reliably recover both first-order and
second-order correlations from the synthetic data
(Fig.~\ref{fig:higher_order_sims}).  When the correlations were stable
for longer intervals (Figs.~\time), or changed gradually (constant, ramping, and
event datasets), recovery performance was relatively high, and we were
better able to recover dynamic first-order correlations than
second-order correlations.  We expected that this would happen, given
that errors in our estimation procedure at lower orders necessarily
propagate to higher orders (since lower-order correlations are used to
estimate higher-order correlations).  Interestingly, we also found
that when the correlations were particularly \textit{un}stable (random
datasets), we better recovered second-order correlations.
